Objectification in Action: Self- and Other-Objectification in Same-gender Interactions

### 2020-09-17 Final_Manuscript.tex
finalizing article

Roberts and Fredrickson (1997) Objectification Theory, suggests that, in
addition to being steeped in a culture that objectifies women, women are
objectified in actual interpersonal encounters. The negative effects of
this interpersonal objectification are theorized be the strongest when
it is a man doing the objectifying (Gervais, Vescio, \& Allen, 2011),
but what are the consequences when a woman objectifies another woman in
an interaction? Psychological researchers studying the sexual
objectification of women, have in recent years explored the
interpersonal process of the objectification, finding evidence for
self-objectification in the target as a proximal consequence (Garcia,
Earnshaw, \& Quinn, 2016, Strelan and Pagoudis (2018), Riemer, Sáez,
Brock, and Gervais (2020)). For example, in a face-to-face mixed-gender
dyadic study, Garcia et al. (2016) found that men's reported
objectification of their female interaction partner was associated with
increased self-objectification reported by their partner. They did not
include same-gender, woman-woman interacting pairs. Gervais, Sáez,
Riemer, and Klein (2020) have reviewed the literature on interpersonal
self-objectification and has organized the process in a theoretical
model called the Social Interaction Model of Objectification (SIMO), but
this model is currently only relevant for mixed-gender encounters.
Although there is ample evidence that women objectify other women
(Loughnan et al., 2015a; Puvia \& Vaes, 2013), there are currently no
studies investigating the process of interpersonal objectification in
same-gender interactions. Does objectification by a female interaction
partner have the same downstream negative consequences as being
objectified by a male interaction partner? The current dyadic study
addresses this omission using interacting pairs where both members
identify as women.

@@

Self-objectification is a psychological process that provides a
cognitive mechanism to translate the experiences of interpersonal
objectification (Loughnan et al., 2015a) to negative mental health
outcomes (e.g., anxiety, self-esteem, and cognitive performance)
(Calogero, Tantleff-Dunn, \& Thompson, 2011; Moradi \& Huang, 2008).
Calogero et al. (2011) proposes that self-objectification can be
conceptualized as a learned trait, or \emph{trait} self-objectification
(TSO). Furthermore, it can also be elicited momentarily, through the
media, for example, with sexualized images in movies and magazines
(Morry \& Staska, 2001), or when wearing sexualizing clothing (B. L.
Fredrickson, Roberts, Noll, Quinn, \& Twenge, 1998). This momentary
self-objectification is referred to as \emph{state} self-objectification
(Bernard, Legrand, \& Klein, 2018; Calogero et al., 2011; Moradi \&
Huang, 2008). Being objectified by another person may interact TSO to
effect experiences of feeling like a body, or state self-objectification
(SSO; Garcia et al., 2016).

@@

Harsey and Zurbriggen (2020) found that self-objectification was related
to the objectification of women to a similar degree for men and women.
Additionally, Strelan and Hargreaves (2005) found that the more women
self-objectify, the more they objectify other women. Could the process
work in the other direction as well, that is, could objectification by a
woman produce self-objectification, in a similar manner to mixed-gender
interactions?

Past research has focused on men's objectifying behaviors, with little
attention paid to the role that women may also play in objectifying
other women. Hill and Fischer (2008) assessed women's experiences of
objectification from men independently from women's experiences of
objectification from other women. They found that women may be
socialized not only to see themselves as objects, but perhaps to see
other women as objects as well. This process, however, was not comfirmed
to occur during an actual interpersonal interaction. Loughnan et al.
(2015a) found that women objectify other women to a greater extent than
they objectify men. Women have also been found to objectify
(dehumanized) sexualized targets presented as images (Puvia \& Vaes,
2013), but very little is known about interpersonal sexual
objectification among women and what the proximal effects of this
objectification might be. We do know that objectification has more
adverse consequences for women than men (Gervais et al., 2011; Moradi \&
Huang, 2008; Saguy, Quinn, F Dovidio, \& Pratto, 2010), however, if
women objectify other women, perhaps even to a stronger degree than they
objectify men, this woman to woman objectification might have
detrimental outcomes.

Studies have shown that within social encounters women are gazed at more
than men (Briton \& Hall, 1995), often times feel \enquote{looked at}
within interpersonal interactions (Argyle \& Williams, 1969;
Miles-McLean et al., 2015), and are likely to internalize the
objectifying gaze on their physical self (Puvia \& Vaes, 2013; Young,
1979). Moreover, perhaps the most adverse effect is that being
objectified socializes girls and women to treat themselves as objects to
be looked at and evaluated (Bartky, 1990; Berger, Cohen, \& Zelditch Jr,
1972; B. L. Fredrickson et al., 1998). Gervais et al. (2020) recently
reviewed the research on interpersonal objectification and organized our
current theoretical understanding of this process in the Social
Interaction Model of Objectification (SIMO). What is clear from Gervais
et al. (2020)'s review is that we know little about women-on-women
interpersonal objectification. Could there also be negative consequences
of this type of interpersonal objectification?

There is evidence that the experience of state self-objectification in
mixed-gender contexts (stranger and romantic) has negative consequences
for women, but what about in the context of interactions with other
women? Is the self-objectification experienced in mixed-gender
interactions associated with the same negative process as that
experienced in same-gender interactions? On the one hand, the ample
research demonstrating that the male gaze has a particularly detrimental
effect would suggest no (Gay \& Castano, 2010; Gervais et al., 2011;
Saguy et al., 2010, Calogero (2004); Yilmaz \& Bozo, 2019), but on the
other hand, women do objectify other women (Harsey \& Zurbriggen, 2020;
Loughnan et al., 2015a; Puvia \& Vaes, 2013). When they do it, does it
lead to self-objectification in the same way men's objectification of
women does (Garcia et al., 2016)? If so, does the self-objectification
experienced in these same-gender interactions have the same negative
consequences for authenticity in that interaction?

\subsection{Interpersonal Objectification and
Authenticity}\label{interpersonal-objectification-and-authenticity}

@@

Data from two demographically equivalent higher education institutions
in the Northeast United States were combined to create the final
analysis sample (\emph{N =} 64) used in this study. In the measures
section that follows we refer to them as Sample 1 and Sample 2.
Thirty-two previously unacquainted self-identifying female dyads (64
total participants) from institutions in the Northeast of the United
States participated in this study. Sample 1 (\emph{N =} 24) is from a
co-ed liberal arts college and Sample 2 (\emph{N =} 40) is from a
women's liberal arts college. More specifically, twelve of the pairs
were students at a co-ed liberal arts college, while the remaining
twenty pairs attended a women's liberal arts college. {[}Footnote:
Initially, data was collected from same-sex and mixed-sex dyads that
comprised of male and female gendered individuals. Sample 1 originally
consisted of twenty-two pairs, twelve men and thirty-two women.
Twenty-three pairs made up of forty-three women and one man, as well as
two participants who did not identify with either gender category,
formed Sample 2. For consistency, we limited participant data to same
sex female pairs at the two colleges.{]} All results presented below are
from models including sample as a control variable.

@@

\subsection{Data analysis}\label{data-analysis}

@@

The current study tested whether the model of interpersonal
objectification and state self-objectification (SSO) used in Garcia et
al. (2016) replicates in a same-gender dyadic sample of women only.
Although past research has found that women do objectify other women
(Harsey \& Zurbriggen, 2020; Loughnan et al., 2015a; Puvia \& Vaes,
2013), this is the first study to test if \emph{interpersonal}
other-objectification by women is related to state self-objectification
in their woman-identified interaction partners. As hypothesized, the
current study did find a significant relationship between a woman's
interaction partner's report of having objectified her and her own
post-interaction feelings of self-objectification. That is, there was a
significant partner effect of other-objectification on SSO. This effect
extends the equivalent relationship found in mixed-gender interactions
to the context of same-gender interactions between women. Thus, evidence
suggests that it is not only the male gaze, and male
other-objectification that is related to women's state
self-objectification, but being objectified by another woman can also
result in SSO, at least in the context of a scenario where they know
they are being evaluated as a potential dating partner. {[}Asha:Or
\ldots{} thus evidence provides support for the claim that women being
objectified by another woman result in sso in ways that are not uniquely
dissimilar from that of xyz{]}

As is the case in all correlational studies, we cannot be sure about the
causal direction. It could be that women's SSO causes them to be
objectified by their interaction partner. This interpretation is
theoretically interesting given that, in both the Garcia et al. (2016)
study and in the current study, it is \emph{women's} SSO that relates to
being objectified by one's partner. However, Objectification Theory
(Roberts \& Fredrickson, 1997), as well as past experimental studies
{[}Saguy et al. (2010); CITE{]}, suggest that the causal flow is from
other-objectification to SSO. Although, the current study found evidence
for the partner effect of other-objectification on SSO, there was a lack
of evidence for the connections between SSO and downstream negative
consequences.

Where the results of the current study diverge most notably from the
results of studies testing interpersonal objectification among
mixed-gender dyads is the lack of evidence for relationships between SSO
and interaction inauthenticity. In addition, we found no evidence of
\emph{direct} or \emph{indirect} relationships between SSO and cognitive
functioning, relationship agency, and career aspirations. Nor was there
evidence of \emph{direct} or \emph{indirect} relationships between
other-objectification and any of these outcomes. This is somewhat
suprising given the extant evidence linking SSO and cognitive
functioning (B. L. Fredrickson et al., 1998; and see Moradi \& Huang,
2008 for a review; Quinn, Chaudoir, \& Kallen, 2011) and the small, but
extant research on interpersonal other-ojectification and cognitive
functioning (Garcia et al., 2016; Logel et al., 2009). This lack of
evidence could potentially signal diverging processes between women's
experiences with interpersonal objectification from men and
interpersonal objectification from women. There is quite a bit of
evidence suggesting that the male gaze is particularly detrimental
(Calogero, 2004; Gervais, Holland, \& Dodd, 2013; Gervais et al., 2011;
Roberts \& Fredrickson, 1997), and perhaps the self-objectification
experienced within an interaction with a women is not as harmful as the
self-objectification experienced within an interaction with a man. As a
strong note of caution, it is best not to interpret a null result as
evidence of no relationship.

The lack of evidence for a relationship between SSO and interaction
authenticity is surprising and again, should not be interpreted as
evidence of no relationship. It should be noted that the estimate of
this relationship was very small, but in the negative direction, as
anticipated. If it is the case that there is a smaller (i.e., weaker)
connection between women's feelings of SSO and inauthenticity in
interactions with other women than in interactions with men, models of
interpersonal objectification, like the SIMO (Gervais et al., 2020),
could be extended by including inauthenticity as a potential mediating
factor. Further, gender of the objectifyer/interaction partner could
also be added to the SIMO model to help understand the circumstances
that require other-objectification and SSO to have negative consequences
for women.

Although we did not find a connection between SSO and authenticity, we
did find significant positive relationships between authenticity and
relationship agency, and authenticity and career aspirations. The
relationship between authenticity and cognitive functioning was also
estimated as positive, but was not statistically signficant. Again, due
to the lack of connection between SSO and authenticity, we found no
evidence of \emph{indirect} relationships between SSO and these outcome
variables. This evidence of a relationship between authenticity and the
relational outcome variables (i.e., relationship agency and career
aspirations) provides evidence that corroborates past findings that felt
authenticity in interactions is important for healthy relationship
functioning (Garcia et al., 2016; Terán et al., 2020). Just as
authenticity has been found to be important in intergroup interactions
(Brunell et al., 2010; Garcia et al., 2016; Tolman et al., 2006), we
again find more evidence here that disruptions in feelings of
authenticity can negatively impact relationships beyond the current
partner. Although the current study did not find a connection between
authenticity and SSO, this seems theoretically to be a natural
connection, and future work must explore when and how SSO leads to
inauthenticity in interpersonal objectification situations.

@@

In addition to being small and combined across two institutions, the
sample of the current study was comprised of Western women, being that
sexual objectification is most prevalent in this culture (Loughnan et
al., 2015b), and research on objectification conducted outside of
Western or Westernized countries is scarce (Moradi \& Huang, 2008),
although more current work examines objectification from a
cross-cultural framework (Loughnan et al., 2015b, Wollast et al.
(2020)). Since \enquote{bodies exist within social and cultural
contexts, and hence are also constructed through sociocultural practices
and discourses} (Roberts \& Fredrickson, 1997, p. 174), it is important
to consider how diverse social identities within unique cultural
contexts may inform sexual objectification phenomenon to test the
cross-cultural applicability of theoretical frameworks (Loughnan et al.,
2015b). Further, sexualizing experiences and self-objectification are
thought to begin a very young age, and thus, researchers have only
recently begun to examine such experiences among children (Bury,
Tiggemann, \& Slater, 2016; e.g., Holland \& Haslam, 2016; Jongenelis,
Byrne, \& Pettigrew, 2014). Considering the fact that the average mean
age of the investigated participants of this current study was 18.85
years, research among younger and older individuals is needed,
especially because self-objectification may change over time (Roberts \&
Fredrickson, 1997). It may be valuable to question the extent to which
children, adolescents, or emerging adults of different races or
ethnicities are exposed to varied amounts of sexualizing content.
{[}Kat: Or a longitudinal study is needed.{]}

@@

The current sample contained a mixture of heterosexual and
non-heterosexual women, but all participants were asked to think about
and evaluate their partner as a potential dating/romantic partner. We
think that hetereosexual women are able to do this with other women as
their target---and there is evidence that they might do this readily
(Puvia \& Vaes, 2013; Strelan \& Hargreaves, 2005)---they may be even
more apt to activate social comparison processes (Festinger, 1954) than
women who are sexually attracted to other women (non-heterosexual
women). This differential psychological process between women with
differing sexualities might have served to dampen our ability to detect
relationships, adding variability. {[}Kat: The only other thing I would
add re: sexuality limitations are that we didn't collect/use sexual
orientation, so we couldn't analyze results by that at all/our samples
might have differed there.{]}

@@

\subsubsection{Measurement}\label{measurement}

Future experiments or longitudinal studies should explore the external
validity of the notions of self-objectification and how the
operationalization of self-objectification may be improved.

\subsubsection{Alternative Model}\label{alternative-model}

Puvia and Vaes (2013) alternative model. TSO -\textgreater{} SOO,
mediated by SSO. \enquote{Found that women's motivation to look
attractive (for men) and internalize sociocultural beauty standards were
positively linked with the dehumanization of sexually objectified female
targets.} Tis relationship was mediated by their own level of
self-objectification.''

\subsection{Clinical Implications}\label{clinical-implications}

>>>>

Roberts and Fredrickson (1997) Objectification Theory, suggests that, in
addition to being steeped in a culture that objectifies women, women are
objectified in actual interpersonal encounters. The negative effects of
this interpersonal objectification for women are theorized be the
strongest when it is a man doing the objectifying (Calogero, 2004; Gay
\& Castano, 2010; Gervais, Vescio, \& Allen, 2011), but what are the
consequences when a woman objectifies another woman in an interaction?
Psychological researchers studying the sexual objectification of women,
have in recent years explored the interpersonal process of the
objectification, finding evidence for self-objectification in the target
as a proximal consequence of being objectified (Garcia, Earnshaw, \&
Quinn, 2016, Strelan and Pagoudis (2018), Riemer, Sáez, Brock, and
Gervais (2020)). In a recent review, Gervais, Sáez, Riemer, and Klein
(2020) organized the extant literature on interpersonal
self-objectification and proposed a theoretical model called the Social
Interaction Model of Objectification (SIMO), however this model focuses
on mixed-gender encounters. Although there is evidence that women
objectify other women (Loughnan et al., 2015a; Puvia \& Vaes, 2013),
there are currently no studies investigating the process of
interpersonal objectification in interactions between women. Is
objectification by a female interaction partner related to an increase
in self-objectification for the woman being objectified? Further, does
objectification by a woman have the same downstream negative
consequences for women as being objectified by a male interaction
partner? The current study begins to address these questions by
investigating interpersonal objectification among interacting pairs
where both partners identify as women.

@@

Self-objectification is a psychological process that provides a
cognitive mechanism to translate the experiences of interpersonal
objectification (Loughnan et al., 2015a) to negative mental health
outcomes (e.g., anxiety, self-esteem, and cognitive performance)
(Calogero, Tantleff-Dunn, \& Thompson, 2011; Moradi \& Huang, 2008).
Calogero et al. (2011) proposes that self-objectification can be
conceptualized as a learned trait, or \emph{trait} self-objectification
(TSO). Furthermore, self-objectification can also be elicited
momentarily, for example, when viewing sexualized images in movies and
magazines (Morry \& Staska, 2001), when trying on sexualizing clothing
(B. L. Fredrickson, Roberts, Noll, Quinn, \& Twenge, 1998), or during
video chat when you believe your interaction partner can only see your
body (not face; Saguy, Quinn, F Dovidio, \& Pratto, 2010). This
momentary self-objectification is referred to as \emph{state}
self-objectification (SSO; Bernard, Legrand, \& Klein, 2018; Calogero et
al., 2011; Moradi \& Huang, 2008) and is characterized by feeling like a
body rather than a full self within a particular moment, instance, or
context (Roberts \& Fredrickson, 1997).

There is evidence that being objectified by another person during an
interaction elicits SSO. For example, in a face-to-face mixed-gender
dyadic study, Garcia et al. (2016) found that men's reported
objectification of their female interaction partner was associated with
increased self-objectification as reported by their female partner.
Further, this negative effect of the men's objectification on women's
SSO was strongest for women higher in TSO. The current study uses this
same dyadic paradigm to study same-gender, woman-woman interacting
pairs.

Studies have shown that within social encounters women are gazed at more
than men (Briton \& Hall, 1995), often times feel \enquote{looked at}
within interpersonal interactions (Argyle \& Williams, 1969;
Miles-McLean et al., 2015), and are likely to internalize the
objectifying gaze on their physical self (Puvia \& Vaes, 2013; Young,
1979). Interpersonal objectification has been found to have negative
consequences for women. Gervais et al. (2011) found that an objectifying
gaze by a male interaction partner (confederate) was associated with
lower math performance for women, than being objectified by a female
interaction partner. Moreover, perhaps the most adverse effect of
interpersonal objectificaiton is that being objectified socializes girls
and women to treat themselves as objects to be looked at and evaluated
(Bartky, 1990; Berger, Cohen, \& Zelditch Jr, 1972; B. L. Fredrickson et
al., 1998). Gervais et al. (2020) recently reviewed the research on
interpersonal objectification and organized our current theoretical
understanding of this process in the Social Interaction Model of
Objectification (SIMO). What is clear from Gervais et al. (2020)'s
review is that we know little about women-on-women interpersonal
objectification. Could there also be negative consequences of this type
of interpersonal objectification?

There is evidence that the experience of state self-objectification in
mixed-gender contexts (stranger and romantic) has negative consequences
for women, but what about in the context of interactions with other
women? Is the self-objectification experienced in mixed-gender
interactions associated with the same negative process as that
experienced in same-gender interactions? The ample research
demonstrating that the male gaze has a particularly detrimental effect
for women would suggest no (Gay \& Castano, 2010; Gervais et al., 2011;
Saguy et al., 2010, Calogero (2004); Yilmaz \& Bozo, 2019), but, there
is evidence that women do objectify other women (Harsey \& Zurbriggen,
2020; Loughnan et al., 2015a; Puvia \& Vaes, 2013) and to would be
helpful to understand the consequencs of this intragroup objectification
for women. When women objectify other women, does it lead to
self-objectification in the same way men's objectification of women does
(Garcia et al., 2016)? If so, does the self-objectification experienced
in these same-gender interactions have the same negative consequences
for authenticity in that interaction?

@@

Past research investigating women objectifying other women has focused
on the psychological conditions that led women to objectify women.
Harsey and Zurbriggen (2020) found that self-objectification was related
to the objectification of women to a similar degree for male and female
participants. Along the same lines, Strelan and Hargreaves (2005) found
that the more women self-objectify, the more they objectify other women.
Could the process work in the other direction as well, that is, could
objectification by a woman produce self-objectification, in a similar
manner to objectification by a man? Hill and Fischer (2008) assessed
women's experiences of objectification from men independently from
women's experiences of objectification from other women. They found that
women may be socialized not only to see themselves as objects, but
perhaps to see other women as objects as well. This process, however,
was not comfirmed to occur during an actual interpersonal interaction.
Loughnan et al. (2015a) found that women objectify other women to a
greater extent than they objectify men. Women have also been found to
objectify (dehumanized) sexualized targets presented as images (Puvia \&
Vaes, 2013), but very little is known about interpersonal sexual
objectification among women and what the proximal effects of this
objectification might be. We do know that objectification has more
adverse consequences for women than men (Gervais et al., 2011; Moradi \&
Huang, 2008; Saguy et al., 2010), however, if women objectify other
women, perhaps even to a stronger degree than they objectify men, this
woman to woman objectification might have detrimental outcomes.

@@

Data from two demographically similar higher education institutions in
the Northeast United States were combined to create the final analysis
sample (\emph{N =} 64) used in this study. In the measures section that
follows we refer to them as Sample 1 and Sample 2. Thirty-two previously
unacquainted self-identifying female dyads (64 total participants) from
institutions in the Northeast of the United States participated in this
study. Sample 1 (\emph{N =} 24) is from a co-ed liberal arts college and
Sample 2 (\emph{N =} 40) is from a women's liberal arts college. More
specifically, twelve of the pairs were students at a co-ed liberal arts
college, while the remaining twenty pairs attended a women's liberal
arts college. {[}Footnote: Initially, data was collected from same-sex
and mixed-sex dyads that comprised of male and female gendered
individuals. Sample 1 originally consisted of twenty-two pairs, twelve
men and thirty-two women. Twenty-three pairs made up of forty-three
women and one man, as well as two participants who did not identify with
either gender category, formed Sample 2. For consistency, we limited
participant data to same sex female pairs at the two colleges.{]} All
results presented below are from models including sample as a control
variable.

@@

@@

The current study tested whether the model of interpersonal
objectification and state self-objectification (SSO) used in Garcia et
al. (2016) replicates in a same-gender dyadic sample of women. Although
past research has found that women do objectify other women (Harsey \&
Zurbriggen, 2020; Loughnan et al., 2015a; Puvia \& Vaes, 2013), this is
the first study to test if \emph{interpersonal} other-objectification by
women is related to state self-objectification in their woman-identified
interaction partners. As hypothesized, the current study did find a
significant relationship between a woman's interaction partner's report
of having objectified her and her own post-interaction feelings of
self-objectification. That is, there was a significant partner effect of
other-objectification on SSO. This effect extends the equivalent
relationship found in mixed-gender interactions to the context of
same-gender interactions between women. Thus, evidence suggests that it
is not only the male gaze, and male other-objectification that is
related to women's state self-objectification, but being objectified by
another woman is also related to women's SSO, at least in the context of
a scenario where they know they are being evaluated as a potential
dating partner.

As is the case in all correlational studies, we cannot be sure about the
causal direction. The model used by the current study asserts that being
objectified by a woman causes women to self-objectify, but it could be
that women's SSO causes them to be objectified by their interaction
partner. This latter interpretation is theoretically interesting given
that, in both the Garcia et al. (2016) study and in the current study,
it is \emph{women's} state self-objectification that relates to being
objectified by one's partner. Objectification Theory (Roberts \&
Fredrickson, 1997), as well as some past experimental studies (Saguy et
al., 2010) suggest that at least one direction of the causal flow is
from other-objectification to SSO. Other studies, especailly those
investigating explicitly women objectifying other women (Puvia \& Vaes,
2013), have relately found evidence that women's \emph{trait}
self-objectification causes women to objectify (dehumanize) other women
and this link is mediated by \emph{state} self-objectification. It could
follow that we tend to objectify other women who objectify us and
through a process of TSO causes SSO which in turn causes objectifation
of one's partner, which in turn causes one's partner to objectify us.
The current study does not provide any evidence of this alternative
model, however---TSO was not significantly correlated with SSO and
actor's objectification was not correlated with partner's
objectification.

Where the results of the current study diverge most notably from the
results of studies testing interpersonal objectification among
mixed-gender dyads is the lack of evidence for relationships between SSO
and interaction inauthenticity. In addition, we found no evidence of
\emph{direct} or \emph{indirect} relationships between SSO and cognitive
functioning, relationship agency, and career aspirations. Nor was there
evidence of \emph{direct} or \emph{indirect} relationships between
other-objectification and any of these outcomes. This is somewhat
suprising given the extant evidence linking SSO and cognitive
functioning (B. L. Fredrickson et al., 1998; and see Moradi \& Huang,
2008 for a review; Quinn, Chaudoir, \& Kallen, 2011) and the research on
interpersonal other-ojectification and cognitive functioning (Garcia et
al., 2016; Gervais et al., 2011; Logel et al., 2009). This lack of
evidence could potentially signal diverging processes between women's
experiences with interpersonal objectification from men and
interpersonal objectification from women. There is quite a bit of
evidence suggesting that the male gaze is particularly detrimental
(Calogero, 2004; Gervais, Holland, \& Dodd, 2013; Gervais et al., 2011;
Roberts \& Fredrickson, 1997), and perhaps the self-objectification
experienced within an interaction with a women is qualtatively
different, and perhaps not as harmful, as the self-objectification
experienced within an interaction with a man. However, as a strong note
of caution, it is best not to interpret a null result as evidence of no
relationship and more research on interpersonal objectification among
women is needed.

The lack of evidence for a relationship between SSO and interaction
authenticity is surprising and again, should not be interpreted as
evidence of no relationship. It should be noted that the estimate of
this relationship was small (close to zero), but in the negative
direction. If it is the case that there is a smaller (i.e., weaker)
connection between women's feelings of SSO and inauthenticity in
interactions with other women than in interactions with men, models of
interpersonal objectification, like the SIMO (Gervais et al., 2020),
could be extended by including inauthenticity as a potential mediating
factor. Further, gender of the objectifyer/interaction partner could be
added as a moderator of the self-objectificaiton to authenticity process
to help understand the circumstances that require other-objectification
and SSO to have negative consequences for women.

Although the current study did not find a connection between SSO and
authenticity, we did find significant positive relationships between
authenticity and relationship agency, and authenticity and career
aspirations. The relationship between authenticity and cognitive
functioning was also estimated as positive, but was not statistically
signficant. Again, due to the lack of connection between SSO and
authenticity, we found no evidence of \emph{indirect} relationships
between SSO and these outcome variables. This evidence of a relationship
between authenticity and the relational outcome variables (i.e.,
relationship agency and career aspirations) provides evidence that
corroborates past findings that felt authenticity in interactions is
important for healthy relationship functioning (Garcia et al., 2016;
Terán et al., 2020). Just as authenticity has been found to be important
in intergroup interactions (Brunell et al., 2010; Garcia et al., 2016;
Tolman et al., 2006), we again find more evidence here that disruptions
in feelings of authenticity can negatively impact relationships beyond
the current partner. Although the current study did not find a
connection between authenticity and SSO, this seems theoretically to be
a natural connection, and future work must explore when and how SSO
leads to inauthenticity in interpersonal objectification situations.

@@

In addition to being relatively small and combined across two
institutions, another limitation of the current study is that the sample
was comprised of Western women only. Being that self-objectification is
most prevalent in Western culture (Loughnan et al., 2015b) research on
objectification conducted outside of Western or Westernized countries
has been scarce (Moradi \& Huang, 2008), although more recent work has
examined objectification from a cross-cultural framework (Loughnan et
al., 2015b, Wollast et al. (2020)). Since \enquote{bodies exist within
social and cultural contexts, and hence are also constructed through
sociocultural practices and discourses} (Roberts \& Fredrickson, 1997,
p. 174), it is important to consider how diverse social identities
within unique cultural contexts may inform sexual objectification
phenomenon to test the cross-cultural applicability of theoretical
frameworks (Loughnan et al., 2015b).

Further, sexualizing experiences and self-objectification are thought to
begin a very young age, and thus, researchers have only recently begun
to examine such experiences among children (Bury, Tiggemann, \& Slater,
2016; e.g., Holland \& Haslam, 2016; Jongenelis, Byrne, \& Pettigrew,
2014). Considering the fact that the average mean age of the
investigated participants of this current study was 18.85 years,
research among younger and older individuals is needed, especially
because self-objectification may change over time (Roberts \&
Fredrickson, 1997). It may be valuable to question the extent to which
children, adolescents, or emerging adults of different races or
ethnicities are exposed to varied amounts of sexualizing content.
Further, more longitudinal studies investigating the developmental
experience of interpersonal objectification and self-objectificaion are
needed {[}see CITE and CITE for exmaples{]}.

@@

The current sample contained a mixture of heterosexual and
non-heterosexual women, but all participants were asked to think about
and evaluate their partner as a potential dating/romantic partner. We
think that hetereosexual women are able to do this with other women as
their target---and there is evidence that they might do this readily
(Puvia \& Vaes, 2013; Strelan \& Hargreaves, 2005)---they may be even
more apt to activate social comparison processes (Festinger, 1954) than
women who are sexually attracted to other women (non-heterosexual
women). This differential psychological process between women with
differing sexualities might have served to dampen our ability to detect
relationships, adding variability.

@@
